Turbulence in compact to giant HII regions

### 2022-05-18 Corr.tex
Javier changes 2022-05-18 morning

\begin{table*}
\begin{center}
\caption{Linear regressions values in the form Y = aX + b between our turbulent parameters obtained using the chi-square statistic and properties of each region (Table \ref{tab:regions-properties}). The fifth column, $r$, is the Pearson correlation coefficient and the last column is the $p$-value. This results were obtained using the procedure in \citet{2007ApJ...665.1489K}.}
\begin{tabular}{cccccc}
\hline
            $Y$ &                   $X$ &                 $a$ &                 $b$ &       $r$ &      $p$ \\
\hline
 log $\sigma$ &            log L(H) &   0.29 $\pm$ 0.09 &  -10.24 $\pm$ 3.53 &   0.89 &  0.001 \\
    log $r_0$ &             log $S$ &   0.78 $\pm$ 0.25 &   -1.31 $\pm$ 0.52 &   0.85 &  0.002 \\
% log $\sigma$ &  log $\sigma_{LOS}$ &   0.83 $\pm$ 0.48 &   -0.24 $\pm$ 0.56 &   0.71 &   0.02 \\
 log $\sigma$ &         log $r_{0}$ &   0.21 $\pm$ 0.17 &    0.66 $\pm$ 0.12 &   0.58 &   0.08 \\
      log $m$ &            log Dist &  -0.09 $\pm$ 0.07 &    1.14 $\pm$ 0.14 &  -0.57 &   0.09 \\
      log $m$ &        log $\sigma$ &  -0.11 $\pm$ 0.21 &    0.07 $\pm$ 0.16 &  -0.42 &   0.23 \\
      log $m$ &         log $r_{0}$ &  -0.04 $\pm$ 0.07 &    -0.0 $\pm$ 0.05 &  -0.39 &   0.26 \\
\bottomrule
\end{tabular}\label{tab:RestStats}
\end{center}
\end{table*}

>>>>

\begin{table*}
\begin{center}
\caption{Linear regressions values in the form Y = aX + b between our turbulent parameters obtained using the chi-square statistic and properties of each region (Table \ref{tab:regions-properties}). The fifth column, $r$, is the Pearson correlation coefficient and the last column is the $p$-value. This results were obtained using the procedure in \citet{2007ApJ...665.1489K}.}
\begin{tabular}{cccccc}
\hline
            $Y$ &                   $X$ &                 $a$ &                 $b$ &       $r$ &      $p$ \\
\hline
 log $\sigma$ &            log L(H) &   0.27 $\pm$ 0.13 &  -9.79 $\pm$ 4.91 &   0.86 &  0.003 \\
    log $r_0$ &             log $S$ &    0.94 $\pm$ 0.3 &  -1.66 $\pm$ 0.66 &   0.85 &  0.004 \\
 %log $\sigma$ &  log $\sigma_{LOS}$ &   0.89 $\pm$ 0.57 &  -0.26 $\pm$ 0.66 &   0.62 &   0.07 \\
 log $\sigma$ &         log $r_{0}$ &   0.17 $\pm$ 0.21 &   0.69 $\pm$ 0.16 &    0.5 &  0.168 \\
      log $m$ &            log Dist &   -0.06 $\pm$ 0.1 &    1.1 $\pm$ 0.21 &  -0.38 &   0.32 \\
      log $m$ &         log $r_{0}$ &  -0.02 $\pm$ 0.09 &  -0.01 $\pm$ 0.07 &  -0.24 &  0.529 \\
      log $m$ &        log $\sigma$ &  -0.05 $\pm$ 0.31 &   0.02 $\pm$ 0.24 &  -0.24 &  0.536 \\
\bottomrule
\end{tabular}\label{tab:RestStats}
\end{center}
\end{table*}
